Btech Project - Progress Diary

### 2017-09-08 Work_report/Daily_progress/work_progress_daily.tex
Extremely minor updates

\subsection{Sept 7 : Thursday}
Minutes of the discussion with professor and my answers to the doubts we previously had.
\begin{itemize}
\item First if the graph structure is approximately the same, we can simply do an adjacency approximation and say that the learned parameters are shared across the graphs.
\item Second if the dimensionality of the vectors in each node is different can go to some fixed length representation using attention mechanism.
\item Third is that if the graph is completely different then we can pass on the laplacian as well. My suggestion and partly intuition is that given a graph signal $x_{G1}$ and graph signal $x_{G2}$ belonging to two different graphs, we should be able to find some kind of conversion using the attention mechanism previously described.
\item Then we go to Sayan's Jigsaw puzzle. The problem is formulated in RNN way with LSTM cells.
\item Need to understand how to apply the graph networks to the subgraph matching problems clearly.
\item Also need to understand seq2seq models. One thing I need to know is to how do we manage the problem of having different length vectors in the seq2seq models.
\item Need to read about : Graph Neural Networks as to how they are different from graph convolution networks in what way and all. Second is to read the gated graph attention mechanism given for alleviating different graph structure problem.
\end{itemize}

>>>>

\subsection{Sept 7 : Thursday}
Minutes of the discussion with professor and my answers to the doubts we previously had.
\begin{itemize}
\item First if the graph structure is approximately the same, we can simply do an adjacency approximation and say that the learned parameters are shared across the graphs.
\item Second if the dimensionality of the vectors in each node is different can go to some fixed length representation using attention mechanism.
\item Third is that if the graph is completely different then we can pass on the laplacian as well. My suggestion and partly intuition is that given a graph signal $x_{G1}$ and graph signal $x_{G2}$ belonging to two different graphs, we should be able to find some kind of conversion using the attention mechanism previously described.
\item Then we go to Sayan's Jigsaw puzzle. The problem is formulated in RNN way with LSTM cells.
\item Need to understand how to apply the graph networks to the subgraph matching problems clearly.
\item Also need to understand seq2seq models. One thing I need to know is to how do we manage the problem of having different length vectors in the seq2seq models.
\item Need to read about : Graph Neural Networks as to how they are different from graph convolution networks in what way and all. Second is to read the gated graph attention mechanism given for alleviating different graph structure problem.
\item Also understood basics of seq2seq model and what attention really is. Just a high level understanding though complete understanding would take a bit more time. Include in basics of beam search algorithm and some ways of doing more seq2seq for not fixed vector lengths.
\end{itemize}

\subsection{Sept 8 : Friday}
\begin{itemize}
\item Started reading about Graph Neural Networks.
\end{itemize}
